\LARGE \bf Grasp Metric for Gaussian Proccess Implicit Surface Representation of Shape Uncertainity

### 2014-07-07 paper.tex
Added more formal bound stuff

We follow the notation of \cite{pokorny2013classical} except that their $\mu$ is our $\tau$ since we use $\mu$ for means.  
We re-state some of their central theorems for our use here.
For more detail, refer there.
$Q(g)$ refers to the exact $L^1$ grasp quality.
It is denoted by the following

@@

@@

\begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||n_i - n_i'||(1+||c_i - z||) \\
					&+ ||(c_i - z)-(c_i'-z')|| \\
					&+ \mu(||n_i - n_i'||(1+||c_i - z||)\\
					&+||(c_i - z)-(c_i'-z')||)
\end{align*}

@@

We now define the concept of a probabilistic bound by functions $\sigma(p)_{n_i}$ and $\sigma(p)_{r_i}$, given a probability $p$ they denote the change in grasp parameter from the mean in the distribution.
$\sigma(p)_{n_i}$ references the distribution defined by $p(n_i = k)$.
$r = c_i - \bar{z}$ defines a moment arm, where $\bar{z}$ is the expected center of mass, then $\sigma(p)_{r_i}$ references the distribution $p(c_i = k)$.
We now write the bound as follows:

 \begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||\sigma_{n_i}(p)||(1+\bar{r}|) + ||\sigma_{r_i}(p)|| \\
                                      &+ \tau(||\sigma(p)_{n_i}||(1+||\bar{r}||)+||\sigma_{r_i}(p)||)
\end{align*}

@@

 \begin{align*}
b_i(p) &= ||\sigma_{n_i}(p)||(1+||\bar{r}||) + ||\sigma_{r_i}(p)|| \\
                                      &+ \tau(||\sigma(p)_{n_i}||(1+||\bar{r}||)+||\sigma_{r_i}(p)||)
\end{align*}

@@

\begin{align}
b(p)  = \max_{i} b_i(p)
\end{align}

@@

we turn to the general case.
$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(p)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(p)$ and $\lambda(x)$ is bounded.
Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.
We can ensure that is true.

>>>>

We follow the notation of \cite{pokorny2013classical} except that their $\mu$ is our $\tau$ since we use $\mu$ for means.  
We re-state some of their central theorems for our use here.
For more detail, refer there.
$Q(g)$ is the exact $L^1$ grasp quality.
It is denoted by the following

@@

The next theorems are used to show that $Q$ is Lipschitz continuous.

@@

\begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||n_i - n_i'||(1+||c_i - z||) \\
					&+ ||(c_i - z)-(c_i'-z')|| \\
					&+ \tau(||n_i - n_i'||(1+||c_i - z||)\\
					&+||(c_i - z)-(c_i'-z')||)
\end{align*}

@@

We now define the concept of a probabilistic bound by functions $\sigma_{n_i}(\zeta)$ and $\sigma_{r_i}(\zeta)$, given a probability $\zeta$ they denote the maximum change in grasp parameter from the mean in the distribution for that probability.
Formally, this is defined as:

\[
  \sigma_{n_i}(\zeta)
  =
  \min_{\mathbb{R}_+}d
\]

\[
  s.t. \ \ \left[ \int_{\mathbb{B}(\bar{n}, d)} p(n_i = k) dk \right] \geq \zeta
\]

and

\[
  \sigma_{r_i}(\zeta)
  =
  \min_{\mathbb{R}_+} d
\]

\[
s.t. \ \ \left[ \int_{\mathbb{B}(\bar{r}, d)} p(r_i = k) dk \right]  \geq \zeta
\]

$\sigma_{n_i}(\zeta)$ references the distribution defined by $p(n_i = k)$.
$r_i = c_i - \bar{z}$ defines a moment arm, where $\bar{z}$ is the expected center of mass, then $\sigma_{r_i}(\zeta)$ references the distribution $p(c_i = k)$.
We now write the above bound as follows:

 \begin{align*}
|l_{i,a,b}(g) - l_{i,a,b}(g')| &\leq ||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||) + ||\sigma_{r_i}(\zeta)|| \\
                                      &+ \tau(||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||)+||\sigma_{r_i}(\zeta)||)
\end{align*}

@@

 \begin{align*}
b_i(\zeta) &= ||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||) + ||\sigma_{r_i}(\zeta)|| \\
                                      &+ \tau(||\sigma_{n_i}(\zeta)||(1+||\bar{r}_i||)+||\sigma_{r_i}(\zeta)||)
\end{align*}

@@

\begin{align}
b(\zeta)  = \max_{i} b_i(\zeta)
\end{align}

@@

we turn to the general case.
$\lambda(x) = \mbox{inf}_{\alpha \in A} f_\alpha(x)$ and $\lambda(x) = \mbox{sup}_{\alpha \in A} f_\alpha(x)$ are bounded with $b(\zeta)$ if $f_\alpha(x)$ for all $\alpha$ is bounded with $b(\zeta)$ and $\lambda(x)$ is bounded.
Since our bound is invariant to the variables $(a,b)$ and we take the maximum set of parameters $i$.
We can ensure that is true.
